### 2016-09-22 paper/extended-example.tex
revised sections 1-5

\dpw{It may be good to hack lstlisting so it can be in a backslash small font.
There is perhaps another environment we could use --- a code environment.}

@@

\subsection{Regular Bijective Lenses}

Once we have a synthesis specification, we need to find a lens that
will convert back and forth between formats and that satisfies the
given examples.  In this paper, we begin our work with a simple and 
relatively standard language of bijective string lens combinators.
In order to guarantee the functions generated by these combinators
form proper bijections between source and target, they are given types using regular expressions.  
We typicallly write 
$\Lens \OfType \Regex \Leftrightarrow \RegexAlt$ to indicate that
a lens $\Lens$ converts back and forth between data belonging
to the languages of regular expressions
$\Regex$ and $\RegexAlt$.

@@

Each of the other lenses manipulate structured data.  For instance,
$\ConcatLensOf{\Lens_1}{\Lens_2}$

@@

\dpw{----------------}

We are trying to synthesize \BibEnd{}.

@@

\begin{figure}
  \Tree[.\textcolor{dkred}{\sout{\texttt{Bib}}}
    [.\textcolor{dkred}{\sout{\texttt{BNames}}}
      \texttt{Name}
      [.\texttt{Names}
        \texttt{Name} ]]]
  \Tree[.\textcolor{dkred}{\sout{\texttt{End}}}
    [.\textcolor{dkred}{\sout{\texttt{ENames}}}
      \texttt{Name}
      [.\texttt{Names}
        \texttt{Name} ]]]
\caption{Marking of Definitions which must be expanded}
\label{fig:expanded-defs}
\end{figure}

Trees of user defined regular expressions,
with those that must be replaced by their definitions crossed out.

After completing these necessary expansions, the problem becomes synthesizing a
lens between the regular expression
\begin{lstlisting}
Bib': ""   | ("author={" Name ", " Name Names (" and " (Name ", " Name Names))* "},")

End': ("%A " (Name Names " " Name) "\n")*
\end{lstlisting}
and

A basic type directed synthesis approach from here will quickly fail.
Both \texttt{Bib'}
and \texttt{End'} are of the form $\Regex_1\Concat\Regex_2$, but there is
not a lens between \texttt{"\%0"} and
\texttt{("@inproceedings" | "@article" | "@book")}.

These issues can be handled by normalizing the regular expressions slightly.
By putting them in a form that normalizes away the equivalences of
associativity, distributivity, and \EmptyString{}.

\begin{lstlisting}
DNFBib':
  ""
  | "author=" Name ", " Name "" Names ""
    (" and " Name ", " Name "" Names "")* ""

DNFEnd':
  "" ("%A " Name "" Names " " Name "\n")* ""
\end{lstlisting}

With those equivalences handled, one might think it is now possible to
synthesize the lens.
Unfortunately, we are still unable to preform any synthesis because the types
on the left and right are quite different, and the lens connectives require
similar types of the left and right.
For example, as \texttt{DNFBib'} has an outer |, we know an or lens must be
synthesized.
However, an or lens requires an outer | on both sides, and \texttt{DNFEnd'} does
not have any outer |.

While, with normalization, certain equivalences have been handled, there are
still many equivalences that haven't been handled.
For example, the star in \texttt{End'} can be unrolled, turning \texttt{End'},
and \texttt{DNFEnd'} into

\begin{lstlisting}
End'': "" | ("%A " (Name Names " " Name) "\n"
("%A " (Name Names " " Name) "\n")*)

DNFEnd'':
  ""
  | "%A " Name "" Names " " Name "\n"
    ("%A " Name "" Names " " Name "\n")* ""
\end{lstlisting}

\texttt{DNFBib'} and \texttt{DNFEnd'} now look very similar.
They both have an outer |, which has on one side a string, and on the other
side, two instances of \texttt{Name}, and an instance of \texttt{Names} outside
of any stars,
with two instances of \texttt{Name}, and an instance of \texttt{Name} underneath
a star.
From this, a lens can easily be made.

However, there is some element of choice in how the lens can be made.
The outer \texttt{Name}s can each be sent to each other.
and the inner \texttt{Name}s can each be sent to each other, so which
should get sent to which.
This can be determined from the examples.
If the first \texttt{Name} in \texttt{DNFBib'} were sent to the first
\texttt{Name} in \texttt{DNFEnd'}, then \texttt{Conway, John} would
get mapped to \texttt{\%a Conway John}, which is inconsistent with the
examples.
The examples can be used, when this situation arises, to specify which parts
of a regular expression can be mapped to which, when the types alone leave
this ambiguous.

\afm{I am not sure going into the metric and priority queue are worth going
  into,
  and least not here?}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

>>>>

@@

\subsection{Regular Bijective Lenses}
\afm{I'm not sure how necessary this section is.  While I want to give users a
  bit of idea about how things map between one another, I think this section
  might go into too much detail.  How would I be able to give the intuition of
  finding parts that map to each other, without just describing lenses (assuming
  that's the right sort of thing to do)?}
Once we have a synthesis specification, we need to find a lens that
will convert back and forth between formats and that satisfies the
given examples.  In this paper, we begin our work with a simple and 
relatively standard language of bijective string lens combinators.
In order to guarantee the functions generated by these combinators
form proper bijections between source and target, they are given types using
regular expressions.  We typically write
$\Lens \OfType \Regex \Leftrightarrow \RegexAlt$ to indicate that a lens $\Lens$
converts back and forth between data belonging
to the languages of regular expressions
$\Regex$ and $\RegexAlt$.

@@

Each of the other lenses manipulate structured data.  For instance,
$\ConcatLensOf{\Lens_1}{\Lens_2}$ operates by applying $\Lens_1$ to the left
portion of a string, and $\Lens_2$ to the right, and concatenating the results.
$\SwapLensOf{\Lens_1}{\Lens_2}$ does the same as $\ConcatLensOf{\Lens_1}{\Lens_2}$
but it swaps the results before concatenating.
$\OrLensOf{\Lens_1}{\Lens_2}$ operates by applying either $\Lens_1$ or $\Lens_2$
to the string.  $\IterateLensOf{\Lens}$ operates by repeatedly applying $\Lens$
to subparts of a string.

@@

\begin{figure}
  \Tree[.\textcolor{dkred}{\sout{\CF{Bib}}}
    [.\textcolor{dkred}{\sout{\CF{BNames}}}
      \CF{Name}
      [.\CF{Names}
        \CF{Name} ]]]
  \Tree[.\textcolor{dkred}{\sout{\CF{End}}}
    [.\textcolor{dkred}{\sout{\CF{ENames}}}
      \CF{Name}
      [.\CF{Names}
        \CF{Name} ]]]
\caption{
Trees of user defined regular expressions,
with those that must be replaced by their definitions crossed out.
}
\label{fig:expanded-defs}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}
Bib':
  "" 
  | ("author={" Name ", " Name Names
    (" and " (Name ", " Name Names))* "},")

End':
  ("%A " (Name Names " " Name) "\n")*
\end{lstlisting}
\label{fig:examples-expanded}
\caption{
  \CF{Bib} and \CF{End} with necessary name replacements preformed.
}
\end{figure}
After completing these necessary expansions, the problem becomes synthesizing a
lens between the regular expressions \CF{Bib'} and \CF{End'} shown in
Figure~\ref{fig:examples-expanded}.

A basic type directed synthesis approach from here will quickly fail.
Both \CF{Bib'}
and \CF{End'} are of the form $\Regex_1\Concat\Regex_2$, but there is
not a lens between \CF{"\%0"} and
\CF{("@inproceedings" | "@article" | "@book")}.

\begin{figure}
\begin{lstlisting}
DNFBib':
  ""
  | "author={" Name ", " Name "" Names ""
    (" and " Name ", " Name "" Names "")* "},"

DNFEnd':
  "" ("%A " Name "" Names " " Name "\n")* ""
\end{lstlisting}
\label{fig:examples-expanded-normalized}
\caption{
  \CF{Bib'} and \CF{End'} put into a semi-normal form.
}
\end{figure}

These issues can be handled by normalizing the regular expressions slightly.
We put them in a form that normalizes away the equivalences involving
associativity, distributivity, and \EmptyString{}, shown in
Figure~\ref{fig:examples-expanded-normalized}

With those equivalences handled, one might think it is now possible to
synthesize the lens.
Unfortunately, we are still unable to preform any synthesis because the types
on the left and right are quite different, and the lens connectives require
similar types of the left and right.
For example, as \CF{DNFBib'} has an outer $\Or$, we know an or lens must be
synthesized.
However, an or lens requires an outer $\Or$ on both sides, and \CF{DNFEnd'} does
not have any outer $\Or$.

\begin{figure}
\begin{lstlisting}
DNFEndUnroll:
  ""
  | "%A " Name "" Names " " Name "\n"
    ("%A " Name "" Names " " Name "\n")* ""

DNFEndMod2:
  ""
      ("%A " Name "" Names " " Name
        "\n%A " Name "" Names " " Name "\n")* ""
  | "%A " Name "" Names " " Name "\n"
      ("%A " Name "" Names " " Name
        "\n%A " Name "" Names " " Name "\n")* ""

\end{lstlisting}
\label{fig:examples-star-equivalenced}
\caption{
  \CF{DNFEnd'} with some star equivalences preformed.
}
\end{figure}

\paragraph*{Step 2:  Traversing Equivalences.}
While, with normalization, certain equivalences have been handled, there are
still many equivalences that haven't been handled.
For example, the equivalences $\StarOf{A}=\EmptyString \Or A\StarOf{A}$ and
$\StarOf{A}=(\EmptyString \Or A)\StarOf{(AA)}$ can be applied to the star in
\CF{End'}, resulting in \CF{DNFEndUnroll} and \CF{DNFEndMod2}, shown in
Figure~\ref{fig:examples-star-equivalenced}.

However, now a single problem of finding a lens between regular expression has
become two problems!  This can be solved by using a priority queue, where the
elements in the queue are regular expression specifications.  The priority of
each specification is a combination of how many expansions have been preformed,
and how different the two regular expressions in the specification are.
\CF{DNFEndUnroll} and \CF{DNFBib'} are very similar, in that they have the same
number of instances of \CF{Name} and \CF{Names}.  However, \CF{DNFEndMod2} is
very different, with a different number of \CF{Name}, \CF{Names}, and a
different number of $\Star$s.  Because of this large difference, the
specification of \CF{DNFBib' <=> DNFEndUnroll} would get popped, instead of the
specification of \CF{DNFBib' <=> DNFEndMod2}.

\paragraph*{Step 3: Creating Lenses.}
Because the regular expressions of  \CF{DNFBib'} and \CF{DNFEndUnroll} are so
similar, type directed synthesis can now happen between them.
Following the types, the outer \CF{""}s
would get mapped to each other, and the sides of the disjunct with $\Star$s
would get mapped to each other.  Within that side, \CF{Name} would map to
\CF{Name}, \CF{Names} would map to \CF{Names} and the $\Star$s would map to the
$\Star$s.

In doing this though, some ambiguity is introduced.  There are two
instances of \CF{Name} present outside a star, so which one should get mapped to
which?  The basic solution would be to map the first to the first, and the
second to the second.  This is not correct, however, as the generated lens for
this will not match the examples.  We can determine which maps to which, as they
must each match the same substrings.  The first \CF{Name} in \CF{DNFBib'}
matches \CF{"Conway"} and the second matches \CF{"John"}.  The first \CF{Name} in
\CF{DNFEndUnroll} matches \CF{"John"} and the second matches \CF{"Conway"}.
This means that the first \CF{Name} in \CF{DNFBib'} must map to the second
\CF{Name} in \CF{DNFEndUnroll}, and vice-versa.  Doing this will generate a lens
that satisfies the type and the examples.

%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2016-09-22 paper/introduction.tex
added variable information on master file to each file
added rough draft of all sections
revised sections 1-5

\begin{enumerate}
\item Search through all possible lenses by: searching for good regular
expressions, then searching within those regular expressions for type directed
lenses
\item Putting the regular expressions in a normal form reduces the number of
regular expressions we must search through
\item Using user defined data types allows the synthesis algorithm to keep the
internals of regular expressions abstracted, unless the internals of those
regular expressions are changed, and the abstraction must be broken.
\item Using a pseudometric on regular expressions, based on the
distribution of user defined data types and size of the regular expression,
allows for an efficient search through equivalent regular expressions
\item We use a data structure combining examples with regular expressions to
synthesize only candidate programs which obey the examples
\item We develop an efficient strategy for finding if two
regular expressions have a lens between them requiring no rewrites which amounts
to merely ordering the components.
\end{enumerate}

In the era of data, big and small, tools for reliably parsing,
printing, cleaning, and transforming data are increasing important.
One class of such tools are \emph{lenses}~\cite{?}, bi-directional
programs that help users solve the classic ``view update problem.''
More specifically, a lens provides a user with two functions, a
\emph{get} function and a \emph{put} function.  The \emph{get}
function translates native data into a new format, or \emph{view}, for
the user.  If the user updates the new view, the corresponding
\emph{put} function can translate the edited data back into
the native format.

One concrete example of where lenses provide value is in managing
linux configuration files.  Such files come in a wide variety of
different ``ad hoc'' data formats, and even experienced system
administrators have a hard time keeping track of all the format
variations.  Moreover, a missing comma, forgotten keyword or 
misplaced vertical bar can cause the systems that depend on such
configurations to crash or misbehave.  In order to manage such configuration
files more reliably,  RedHat developed Augeas~\cite{}, a configuration
editing system based around lenses.  At the moment, Augeas contains more
than 200 stock lenses to provide views of common configuration files.

Lenses are popular because they typically come with strong guarantees
about the get-put (or put-get) round-trip behavior.  Such guarantees
help users guard against data corruption while reading and editing
high-value data sources.

>>>>

The growing dependence on big data makes tools for reliably parsing,
printing, cleaning, and transforming data increasing important.
One such class of tools are \emph{lenses}~\cite{Focal2005-long}, bi-directional
programs that help users solve the classic ``view update problem.''
More specifically, a lens provides a user with two functions, a
\emph{get} function and a \emph{put} function.  The \emph{get}
function translates native data into a new format, or \emph{view}, for
the user.  If the user updates the new view, the corresponding
\emph{put} function can translate the edited data back into
the native format.

Bidirectional programming is used heavily in practice.
Augeas~\cite{?}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
Bixid~\cite{?} is a language developed for expressing bidirectional XML
transformations.
XSugar~\cite{?} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{?} and Leiden+~\cite{?} formats for
encoding ancient documents~\cite{?}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.

Lenses are popular because they typically come with strong guarantees
about the get-put (and put-get) round-trip behavior.  Such guarantees
help users guard against data corruption while reading and editing
high-value data sources.  These guarantees are often achieved through
the use of domain-specific languages with strong type systems that
guarantee invertability of lens programs~\cite{?,?,?}.  Unfortunately, such
lens languages are currently quite non-standard.  The
process of writing a lens is challenging, as a user must think
about data conversion in two directions at once --- an
unusual task for the everyday programmer.  As a consequence, 
for the casual user of lenses, learning the language, its type system and its
unorthodox programming style is time-consuming and, in the end,
a disincentive to adopting the technology, despite its advantages.

In order to overcome the steep learning curve involved in programming
with lenses, we have developed a new system for synthesis of lenses
from their types and a collection of representative examples.  More
specifically, we focus on algorithms for the synthesis of bijective
string lenses.  The types for such lenses are regular expressions,
which describe the format of the source and target strings.  Given
such types, and a very small number of representative examples (sometimes
no examples at all), we synthesize a well-typed lens that implements
a bijection between data formats.

Recently, researchers have developed a number of new algorithms for
type-directed synthesis~\cite{?,?,?}.  Many of those
algorithms~\cite{osera+:pldi15,frankle+:popl16,armando+:pldi16} are
directed in part by the syntax of types.  For instance, to find an
expression with type $A \rightarrow B$, such algorithms will assume
that the expression in question is a function with the form $\lambda
x{:}A. e$, and they will continue the search for an expression $e$
with type $B$ under the hypothesis that the parameter $x$ has type
$A$.  In the case of the simply-typed lambda calculus, such an
approach reduces the complexity of the search for terms inhabiting the
type without losing completeness.  Lenses are defined by a richer type system
than the simply typed lambda calculus,
with their regular expression types, as
there are many equivalent ways to express the same regular expression.
Unfortunately, this makes simple
syntax-directed algorithms not directly applicable.

\paragraph*{The Central Challenge.}
To illustrate the central challenge facing the design of our synthesis system
in greater detail,
consider the concatenation lens, $\Lens_1 \Concat \Lens_2$,
one of the simplest string lens combinators.  
When viewed from left to right, this lens defines a function \emph{get}, which,
given a string 
$\String$, divides $\String$ into two substrings $\String_1$ 
and $\String_2$, applies $\Lens_1$ to the first, yielding $t_1$,
and $\Lens_2$ to the second, yielding $t_2$.  When viewed from
right to left, it defines a second function \emph{put}, which maps
data back from strings $t$ to strings $s$ in an analogous way.

The type system for lenses ensures such \emph{get} and \emph{put} functions
satisfy strong invertibility properties.  In our case, the two functions
form a bijection.  In general, to 
describe the type of a lens, we write $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, which may be read ``lens $\Lens$ converts back and forth between
data in the language of regular expression $\Regex$ and data in the language
of regular expression $\RegexAlt$''.  More specifically, to give a type
to the concatenation lens, we use the following typing rule.
\[
\inferrule
{
\Lens_1 \OfType \Regex_1 \Leftrightarrow \RegexAlt_1\\
\Lens_2 \OfType \Regex_2 \Leftrightarrow \RegexAlt_2\\\\
\UnambigConcatOf{\Regex_1}{\Regex_2}\\
\UnambigConcatOf{\RegexAlt_1}{\RegexAlt_2}
}
{
\ConcatLensOf{\Lens_1}{\Lens_2} \OfType \Regex_1\Regex_2 \Leftrightarrow \RegexAlt_1\RegexAlt_2
}
\]
Above, the notation $\UnambigConcatOf{\Regex_1}{\Regex_2}$ asserts that $\Regex_1$ and $\Regex_2$ are
unambiguously concatenable, meaning there is
exactly one way to divide up any
string $\String$ in the language of $\Regex_1\Regex_2$ into $\String_1$
and $\String_2$ such that $\String_1$ is in the language of $\Regex_1$
and $\String_2$ is in the language of $\Regex_2$.  These unambiguous
concatenation constraints guarantee the \emph{get} and \emph{put}
functions are indeed functions and that they form a bijection if
the underlying lenses are bijective.

Now, with these typing rules in hand, consider trying to search for
a lens with the type $(A B) C \Leftrightarrow A' (B' C')$ where
we know of lenses with types 
$A \Leftrightarrow A'$, $B \Leftrightarrow B'$, and 
$C \Leftrightarrow C'$.  A straightforward,
syntax-directed search suggests applying the rule for concatenation,
and looking for two simpler lenses with the types $A B \Leftrightarrow A'$
and $C \Leftrightarrow B' C'$ respectively.  Unfortunately, at this point,
we are simply stuck---we have no lenses with those types.  Of course,
the natural
solution to this problem
is to introduce a type conversion rule to the system:
\[
\inferrule
{
\Lens \OfType \Regex_1 \Leftrightarrow \Regex_2\\
\Regex_1 \equiv \Regex_1'\\
\Regex_2 \equiv \Regex_2'
}
{
\Lens \OfType \Regex_1' \Leftrightarrow \Regex_2'
}
\]
With such a type conversion rule, we could first 
convert the type $(A B) C \Leftrightarrow A' (B' C')$
to the better aligned $(A B) C \Leftrightarrow (A' B') C'$.
When we then proceed with structure decomposition using the
concatenation rule, we generate sub-problems involving
finding lenses for types
$A \Leftrightarrow A'$, $B \Leftrightarrow B'$, and 
$C \Leftrightarrow C'$, which is just what we had in hand.

Because equivalence of regular expressions is decideable, when
given a lens $\Lens$ with type $\Regex_1 \Leftrightarrow \Regex_2$,
it is easy to \emph{check} whether that lens also has type 
$\Regex_1' \Leftrightarrow \Regex_2'$, and lens programming languages
such as Boomerang \cite{foster:thesis} do so.  However, 
when we turn to synthesis and are given the lens type 
$\Regex_1' \Leftrightarrow \Regex_2'$ and the option to apply this
rule, the search space becomes unmanageably large --- we must guess
some arbitrary new regular expressions $\Regex_1$ and $\Regex_2$ that are
equivalent to  $\Regex_1'$ and $\Regex_2'$ respectively
and there are infinitely many such regular expressions to choose
from.

Furthermore, the language of lenses without a composition operator is not closed
under composition.  There exists lenses $\Lens_1 \OfType \Regex_1 \Leftrightarrow
\Regex_2$, $\Lens_2 \OfType \Regex_2 \Leftrightarrow \Regex_3$ where there is no
lens $\Lens \OfType \Regex_1 \Leftrightarrow \Regex_3$ such that
$\SemanticsOf{\ComposeLensOf{\Lens_2}{\Lens_1}}=\SemanticsOf{\Lens}$.  So, if we
would like to be able to synthesize $\ComposeLensOf{\Lens_2}{\Lens_1} \OfType
\Regex_1 \Leftrightarrow \Regex_3$ then we
must also search through possible $\Regex_2$ for creating compositions.

In essence,
we must solve the problem of search \emph{in three dimensions}:  In one
dimension, we must search for a regular expression \emph{type}
with an appropriate ``syntactic shape''.  In a second dimension,
we must search for a lens \emph{expression} that has the given type and
is consistent with the user's examples.  In a final dimension, we must search
for intermediary regular expressions for composing lenses.

\paragraph*{Our Solution.}  Our solution to this problem is to define
a new language of lenses that
cuts down the synthesis search space \emph{in all dimensions}.
This language is designed so that its regular expression types are limited 
to those in a pseudo-canonical form.  This pseudo-canonical form
demands that regular expressions be defined as a flattened 
union of concatenated strings and atoms, where each atom is a user defined data
type or the Kleene star of an expression that is recursively in normal form.
When converted into this pseudo-canonical form, two regular expressions that 
differed only by associativity of concatenation will be syntactically equal.
For example, rather than searching for a lens with type 
 $(A B) C \Leftrightarrow A' (B' C')$, our algorithm will always search
for one with type  $(A B) C \Leftrightarrow (A' B') C'$

More generally, many, but not all, structural incongruities that
prevent the existence of lenses disappear.
Not all structural incogruities disappear because our regular expressions
are only \emph{pseudo-canonical}.  For instance, our pseudo-normal form
does not automatically unify lenses such as
$A B* \Leftrightarrow A (\epsilon + BB*)$ that result from an
unrolling of Kleene Star, for instance.
Consequently, we structure our synthesis algorithm in two parts:  The
first is a syntax-directed search for a lens based on the structure of the given
regular expression types and, if that fails, the second is a search,
using Conway's axioms~\cite{conway} for 
equivalent regular expression types that might allow a new search
in the first phase of the search to succeed.

Furthermore, in this new language, we can express transformations which were
previously inexpressible without composition.  It is still an open problem
whether this new language is closed under composition.  However, with the
increased expressibility, we have found searching for a central regular
expression to compose with to be unnecessary in practice.

The types
describing data formats may be very large --- they are regular
grammars describing complex data formats.  This is another complication that
arises in this synthesis setting, but not elsewhere in the literature on type
directed synthesis.  On the one hand, this is
very useful as such types provide a wealth of information that constrains
the search process effectively.  On the other hand, there is a lot of
data that must be managed carefully by the synthesis system.
One important observation is that users naturally construct
such types compositionally, using named abbreviations for subcomponents.
The structure inherent in these named abbreviations can be 
exploited by the synthesis algorithm to speed up the search dramatically.

For example, if the name $A$ appears once on both the left and the right,
the system will hypothesize that the identity lens can be used to convert
between occurrences of $A$.  On the other hand, if the name $A$ appears
on the left, but not on the right, the system will determine that the
name $A$ should be replaced by its definition.  Likewise, differing
numbers of occurrences of names can serve as a guide for unrolling
Kleene star or applying other regular expression equivalence axioms.
Hence, in general, to guide the transformation of regular expression
types, we define a pseudometric based on the occurrence of names.

\paragraph*{Contributions.}  We have designed and implemented
a new system for the synthesis of bijective string lenses.
In addition, this paper makes the following contributions:

\begin{itemize}
\item It defines a new language of lenses designed specifically for synthesis
with types based on pseudo-canonical regular expressions, with a term 
language to match.
\item We formalize the semantics of the language and prove it sound with
respect to an existing, standard language for bijective string lenses.
\item We designed a type-directed, two-dimensional 
algorithm for synthesizing lenses in our new domain-specific language.
\item We developed a collection of optimizations that speed up the basic
synthesis algorithm.
\item We have implemented the language and evaluated it on a range of
over 40 benchmarks including micro-benchmarks, a few examples from FlashFill,
and a number of examples from the Augeas system for transforming linux
file formats.  Our synthesis algorithm succeeds on all of our
benchmarks.  When it succeeds, synthesis time is typically less than 1 second.
\end{itemize}

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
